\section{Summary}

Auto-scaling is of vital importance to realize the full potential of cloud computing. However, current auto-scaling solutions available in PaaS cloud remain primitive. Almost all the PaaS providers rely on reactive approach and lacks workload awareness needed for detailed decision making and rely on rule-based decision making which expects users to set threshold parameters. To address these problems, we proposed auto-scaling solution called inteliScaler with an ensemble workload prediction mechanism based on time series and machine learning techniques, scaling algorithm that considers both cost and QoS factors when deciding the amount of resources required, and pricing model-aware decision making. We tested the proposed model in two levels. First, we evaluated the performance of individual components on simulation set-up with various workload datasets available. Second, we developed an entire solution on Apache Stratos PaaS framework and tested with a deployment on Amazon EC2. Empirical results in both levels show significant benefits for PaaS users. It is possible to improve the proposed heuristic by introducing different penalty functions  based on the level of service expected by different users. For example, an application (deployed on a PaaS) that supports free as well as paid versions would require different service levels. Our proposed solution can be adapted for such scenarios by defining different penalty functions based on the type of subscription.\\