In this paper we present the design, implementation and evaluation of inteliScaler, which is a workload and resource aware, proactive auto scaler for the open cloud platform-as-a-service (PaaS). Our solution overcomes the inadequacy and inefficiency in the existing PaaS auto scalers which prominently operate on top of rule based engines. Simulation results using the RUBiS application and empirical workload traces show significant cost and energy savings by inteliScaler compared to a typical PaaS auto scaler.

Cloud systems rely on virtualization techniques to provide computing resources on demand. Elasticity is a key feature where provisioning and de-provisioning of resources is done via auto-scaling. However, in most of the platform-as-a-service (PaaS) systems, autoscaling solutions are based on reactive, threshold-driven approaches. Such systems are incapable of catering to rapidly varying workloads, unless the associated thresholds are sufficiently low; however, maintaining low thresholds introduces the problem of over-provisioning under relatively stable workloads. Determining an optimum threshold which solves these issues while minimizing costs and meeting QoS demands is not a trivial task for a regular PaaS user. On the other hand, thresholds are not a good indication of QoS compliance, which is a key performance indicator of a cloud application.

In this paper we propose inteliScaler, a proactive and cost-aware autoscaling solution to address the above issues by combining a predictive model, cost model and a smart killing feature. We introduce an ensemble workload prediction mechanism based on time series and machine learning techniques for making accurate predictions on drastically different workload patterns. Simulation results using the RUBiS application and empirical workload traces show significant cost savings by inteliScaler compared to a typical PaaS auto scaler. We have also evaluated our approach by implementing it on Apache Stratos PaaS and deploying and testing it on AWS EC2. Results show significant QoS improvements and cost reductions relative to a typical reactive and threshold-based PaaS autoscaling solution.